### 2020-05-31 writeup/proof_examples.tex
sec 3.2

>>>>

\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
	In the isotropic model, assume that $\rho_1,\rho_2 > 10$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
	Then the data efficiency ratio is at least \[ \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{\rho_1^{-1} + \rho_2^{-1} - 5\Psi(\beta_1, \beta_2)}}. \]
\end{proposition}

### 2020-05-31 writeup/transfer.tex
sec 3.2

We use our tools to explain a key result of Taskonomy by Zamir et al.'18 \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed from each task to achieve comparable performance to STL.
Formally, let the data efficiency ratio be the largest factor $x$ such that the total number of labeled datapoints needed for solving all tasks can be reduced by $x$ while keeping the same performance compared to STL.
%More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using only $x \cdot n_i$ datapoints from every task.
The data efficiency ratio is defined as
\[ \argmin_{x\in(0, 1)} ~~
		\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))
		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]

\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
	In the isotropic model, assume that $\rho_1,\rho_2 > 10$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
	Then the data efficiency ratio is at least \[ \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{\rho_1^{-1} + \rho_2^{-1} - 5\Psi(\beta_1, \beta_2)}}. \]
\end{proposition}
The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.

\textbf{Algorithmic consequence.} An interesting consequence of Proposition \ref{prop_data_size} is that the $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho$.
Instead, from the analysis, we observe that $L(\hat{\beta}_t^{\MTL})$ is quadratic.
Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
Algorithm \ref{alg_inc_train} shows the procedure.

\begin{algorithm}[!t]
	\caption{An incremental training schedule for multi-task learning}
	\label{alg_inc_train}
	\begin{algorithmic}[1]
		\State as
	\end{algorithmic}
\end{algorithm}
\subsection{Covariate Shift}

>>>>

\textbf{Connection to Taskonomy.} We use our tools to explain a key result of Taskonomy by Zamir et al.'18 \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed to achieve comparable performance to STL.
Formally, let the data efficiency ratio be the largest factor $x$ such that the total number of labeled datapoints needed for solving all tasks can be reduced by $x$ while keeping the same performance compared to STL.
%More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using only $x \cdot n_i$ datapoints from every task.
The data efficiency ratio is defined as
\[ \argmin_{x\in(0, 1)} ~~
		\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))
		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]
Using our tools, we show that in the isotropic model, the data efficiency ratio is
equal to \[ \frac{1}{\rho_1 + \rho_2} {+ \frac{1}{(\rho_1 +\rho_2)(\rho_1^{-1} + \rho_2^{-1} - \Theta(\Psi(\beta_1, \beta_2)))}}. \]
In addition to $\rho_1,\rho_2$, the data efficiency ratio also scales with $\Psi(\beta_1, \beta_2)$, the model distance between the tasks.
The result can be found in Appendix \ref{app_proof_data}.

\textbf{Algorithmic consequence.} An interesting consequence of Proposition \ref{prop_data_size} is that $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho_1$.
In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
Algorithm \ref{alg_inc_train} describes the procedure.

\begin{algorithm}[!t]
	\caption{An incremental training schedule for multi-task learning over two tasks}
	\label{alg_inc_train}
	\begin{algorithmic}[1]
		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
		\Req Batch size $S$, number of epochs $T$, validation accuracy $\hat{g}(B; W_1, W_2)$.
		\State Divide $(X_1, Y_1)$ randomly into $K$ batches of size $S$ as $(x^{(1)}, y^{(1)}), \dots, (x^{(K)}, y^{(K)})$.
		\For{$i = 1,\dots, K$}
			\For{$j = 1,\dots, T$}
				\State Update $B, W_1, W_2$ using the training data $\set{x^{(j)}, x^{(j)}}_{j=1}^i$ and  $(X_2, Y_2)$.
			\EndFor
		\State Let $a_i = \hat{g}(B; W_1, W_2)$ be the validation loss after epoch $i$.
			If $a_i < a_{i+1}$, \textbf{break}.
		\EndFor
	\end{algorithmic}
\end{algorithm}

\subsection{Covariate Shift}
